---
title: "Week 4 - in class discussion materials"
output: html_notebook
---
# Measurement Process Characterization

## Where is ggplot being used?

Recent article on [GDP](https://www.nytimes.com/2018/01/26/business/economy/gdp-economy.html)

Recent article on the [economy](https://www.vox.com/policy-and-politics/2018/1/30/16945386/trump-economy-state-of-the-union)

Recent article on [science education](http://physicstoday.scitation.org/doi/10.1063/PT.3.3816)

>The nine lab courses covered both mechanics and electricity and magnetism; and they used algebra- and calculus-based approaches. They were offered at 3 institutions, taught by 7 instructors, and taken by nearly 3000 students. 


## 2.4 Gauge R & R studies

```{r}
library(tidyverse)
```


***

### Important issues

- Repeatability - precision
- Reproducibility - day-to-day variability
- Stabiiltiy - run-to-run 
- Bias - "systematic error"


### Design considerations

- Artifiacts (check standards)
- Operators
- Gauges
    - Parameter levels
    - Configuraitons

***

### Analysis of repeatability
- Plot of repeatability standard deviations versus check standard with day coded
- Plot of repeatabaility standard deviation versus check standard with gauge coded

***
Data:  
Column 1:   Run Number (1 or 2)  
Column 2:   Wafer ID (check standards 138, 139, 140, 141, 142)  
Column 3:   Probe (1, 281, 283 2062, 2362)  
Column 4:   Month  
Column 5:   Day  
Column 6:   Operator (1 or 2)  
Column 7:   Temperature  
Column 8:   Average of Resistivity Measurements  
Column 9:   Standard Deviation of Resistivity Measurements  

***

```{r read mpc61 data}
mpc61a_clean <- read_csv('mpc61a_clean.csv')
mpc61a_clean
```

              
***

### Define s1 based on the pooled statndard deviation of the stdev column

```{r s1}
s1_mpc61 <- sqrt(mean(mpc61a_clean$stdev^2))
s1_mpc61
```

### Plot the stdev by wafer, coded by day for each run

Here are the NIST plots:

[2.6.1.2 Repeatability standard deviations](http://www.itl.nist.gov/div898/handbook/mpc/section6/mpc613.htm)


```{r repeatability by wafer}
ggplot(mpc61a_clean) +
  geom_point(aes(x = wafer, y = stdev, colour = day)) +
  facet_wrap(~ run)

```

***

###
Issues?

I don't like the continuous scale. This meeans we would need to set the days as factors.

```{r run repeatability by wafer and day}
ggplot(mpc61a_clean) +
  geom_point(aes(x = wafer, y = stdev, colour = as.factor(day))) +
  facet_wrap(~ run)
```

***
I don't really need to know the actuall days, I just want to compare days. So I can turn off the legend. I also prefer the theme_bw()

```{r run repeatability by wafer and day rev2}
ggplot(mpc61a_clean) +
  geom_jitter(aes(x = wafer, y = stdev, colour = as.factor(day)), width = 0.2, height = 0) +
  facet_wrap(~ run) +
    theme(legend.position = "none", panel.background = element_rect(fill = "white", linetype = "solid", colour = "black"), panel.grid.major = element_line(colour = "grey90"))
  
```

***
or

```{r keep it simple}
ggplot(mpc61a_clean) +
  geom_jitter(aes(x = wafer, y = stdev, colour = as.factor(day)), width = 0.2, height = 0) +
  facet_wrap(~ run) +
    theme(legend.position = "none") + 
  labs(caption = "color coded by day")
```

***

### Repeat the above steps, but color code by probe

```{r }
ggplot(mpc61a_clean) +
  geom_jitter(aes(x = wafer, y = stdev, colour = as.factor(probe)), width = 0.2, height = 0) +
  facet_wrap(~ run) +
  labs(colour = "probe")
```

```{r}
ggplot(mpc61a_clean) +
  geom_jitter(aes(x = wafer, y = stdev, colour = as.factor(probe)), width = 0.2, height = 0) +
  facet_grid(run ~ probe) +
  labs(colour = "probe")
```


***

### Analysis of reproducibility and stability  
#### Effects of days and long-term stability  

[2.6.1.4 Effects of days and long-term stability](http://www.itl.nist.gov/div898/handbook/mpc/section6/mpc614.htm)

For each wafer, I'd like to look at the reproducability and long-term stability

```{r reproducability and long-term stability, echo=TRUE}
ggplot(mpc61a_clean) +
  geom_point(aes(x = date_time, y = average, colour = as.factor(run))) +
  facet_grid(wafer ~ probe, scales = "free_y") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(colour = "run") 
```

***

### Analysis of bias (????)
#### Differences among gauges

[2.6.1.5 Differences among 5 probes](http://www.itl.nist.gov/div898/handbook/mpc/section6/mpc615.htm)

```{r}
ggplot(mpc61a_clean) +
  geom_point(aes(x = wafer, y = average, colour = probe)) +
  facet_grid(wafer ~ run, scales = "free_y")
```

```{r}
ggplot(mpc61a_clean) +
  geom_boxplot(aes(x = as.factor(probe), y = average)) +
  facet_grid(wafer ~ run, scales = "free_y")
```

```{r}
ggplot(mpc61a_clean) +
  geom_boxplot(aes(x = as.factor(probe), y = stdev)) +
  facet_grid(wafer ~ run, scales = "free_y")
```

### SixSigma
```{r}
library(SixSigma)
ss.rr(var = average, part = wafer, appr = probe, data = mpc61a_clean, main = "SixSigma analysis of MPC61.DAT file", sub = "for MST 6600")

```




```{r}
ss.rr(var = average, part = run, appr = probe, data = mpc61a_clean, main = "SixSigma analysis of MPC61.DAT file", sub = "for MST 6600 test")
```

Go back to RStudio for SixSigma

****

### Looking aheaad (R for Data Science: Chapter 5 - Data Transformation)

#### Look at Guage R & R data

* Principles of tidy data **tidyr** package (part of the **tidyverse** package)
    * Most common
        * spread()
        * gather()
    * Less common
        * separate()
        * unite()
* Data transfomration with the **dplyr** package (part of the **tidyverse** package)
    * Most common
        * filter()
        * mutate()
        * group_by() & summarise()
    * less common for visulazation
        * arrange()
        * select()
        * rename()

### Examples using the `mpc61_clean` data

#### Using the `filter()` function

```{r}
mpc61_probe2062 <- filter(mpc61a_clean, probe == 2062)
mpc61_probe2062
```

### Analysis using new data frame

```{r}
ggplot(mpc61_probe2062) +
  geom_jitter(aes(x = wafer, y = stdev, colour = as.factor(run)), width = 0.2, height = 0) +
  labs(colour = "run")
```


#### comparison of best and worst

From the SixSigma work (and visually) we saw that 2062 was the worse performing probe and 2362 was one of the best. 

```{r}
mpc61_probes_good_bad <- filter(mpc61a_clean, probe == c(2062, 2362))
mpc61_probes_good_bad
```


```{r}
ggplot(mpc61_probes_good_bad) +
  geom_jitter(aes(x = wafer, y = stdev, colour = as.factor(run)), width = 0.2, height = 0) +
  facet_wrap(~ probe) +
  labs(colour = "run")
```

#### group_by() & summarise()

We've been able to make some great graphics, but what about hte numbers!
(Editoral comment: Someone will always ask for a summary report, even if the graphics clearly show the answer.)

```{r}
by_wafer <- group_by(mpc61a_clean, wafer)
by_wafer
```

```{r}
mpc61a_clean
```

It doesn't look like anything has changed, but R has grouped the data by wafer. We can see this when we use the `summarise()` function.

```{r}
wafer_summary <- summarise(by_wafer, average = mean(average))
wafer_summary
```

```{r}
ggplot(wafer_summary) +
  geom_point(aes(x = as.factor(wafer), y = average))
```

#### We aren't limited to grouping by a single variable

```{r}
by_wafer_probe <- group_by(mpc61a_clean, wafer, probe)
by_wafer_probe
```

#### Again, the data frame looks the same; however, 
```{r}
wafer_probe_summary <- summarise(by_wafer_probe, sd_ave = sd(average), n = n())
wafer_probe_summary
```

```{r echo=TRUE}
ggplot(wafer_probe_summary) +
  geom_bar(aes(x = as.factor(wafer), y = sd_ave, fill = as.factor(probe)), stat = "identity") +
  facet_grid(. ~ probe) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(fill = "probe", x = "wafer", y = "standard deviation of the average, s2") 
```

